Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/introduction.tex
Update introduction.tex
Shortened a footnote to save one line

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
%%%%%
It is also known that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case.
These results guarantee that the \textsc{Multiclass Perceptron} achieves an
information-theoretically optimal mistake upper bound, meanwhile it has
low time and memory complexities.%
%The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
%since it achieves an information-theoretically optimal mistake upper bound,
%while having low time and memory complexities.
%%%%%
~\footnote{These are
folklore results. For completeness, we present these results along
with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
supplementary material.}

>>>>

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
%%%%%
It is also known that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case.
These results guarantee that the \textsc{Multiclass Perceptron} achieves an
information-theoretically optimal mistake upper bound, meanwhile it has
low time and memory complexities.%
%The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
%since it achieves an information-theoretically optimal mistake upper bound,
%while having low time and memory complexities.
%%%%%
~\footnote{
%%%%%
%These are folklore results. 
For completeness, we present these 
folklore
%%%%%
results along
with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
supplementary material.}
